An ultra-low noise, high-voltage piezo driver

### 2016-05-31 piezo.tex
Formatting changes; added LP filter switch to schematic

The low-noise stabilization circuit is crucial to the performance of the design, as it is responsible for removing noise at the output of the flyback converter.
To accomplish this task, a high slew-rate op-amp (Texas Instruments LM7171, \SI{4100}{\volt\per\micro\second}) drives the galvanically isolated ground node of the flyback converter (see U2 in Fig.~\ref{Fig:PiezoCircuit}).
This op-amp enforces the HV output voltage
\begin{align}
\text{V}_\text{HV} &= \left(1 + \frac{R_1}{R_2~||~R_\text{mod}}\right) \text{V}_\text{DC} -
\left(\frac{R_\text{mod}}{R_1}\right) \text{V}_\text{mod}
\end{align}
We choose $R_1, R_\text{mod} = \SI{1}{\mega\ohm}$, $R_2 = \SI{20.5}{\kilo\ohm}$ such that the DC gain is $\approx 50$ and the modulation gain is unity.
Depending on the application, however, other gain configurations would work equally well provided the non-inverting gain of U2 closely matches the gain of the flyback regulator since they derive from the same control voltage.
Ultimately, the op-amp U2 sets the operating voltage of the output referenced to true circuit ground, while the flyback converter regulates the high voltage relative to the pseudoground node $\text{GND}_\text{HV}$.
Because the output of the flyback regulator is galvanically isolated, U2 is free to control the $\text{GND}_\text{HV}$ node at ``low'' voltages, which are transferred directly to the high voltage output.

@@

\begin{figure}[t]
\includegraphics[width=\columnwidth]{fig/NoiseModel.ai}
\caption{Noise model. \label{Fig:NoiseModel}}
\end{figure}

We analyze the noise performance of the circuit according to the model shown in Figure~\ref{Fig:NoiseModel}, where noise spectral densities are calculated at the node HV.
Here, we consider contributions from the intrinsic op-amp noise, the DAC (injected at the node $V_{\text{DC}}$), Johnson-Nyquist noise of the passive components, and any additional noise injected at the modulation input node $V_{\text{mod}}$.
We also discuss, given our choice of op-amp, the noise rejection ratio from the DRV2700 flyback regulator.

First, the noise gain ($NG$) for this amplifier configuration is given by
\begin{align}
\label{Eq:NG}
%NG(s) &= 1 + \frac{R_1 \epar C_1}{R_2 \epar \left(R_{\text{mod}} \epar C_{\text{mod}}\right)}
%NG(s) &= 1 + \frac{R_1~||~C_1}{R_2R_{\text{mod}} C_{\text{mod}}}
NG(s) &= 1 + \frac{Z_1}{R_2 \epar Z_{\text{mod}}}
\end{align}
where we've defined the equivalent impedances $Z_1 = R_1/(1+R_1 C_1 s)$ and $Z_{\text{mod}} = R_{\text{mod}}/(1+R_{\text{mod}} C_{\text{mod}} s)$, and $s = i\omega$ is the frequency in the Laplace domain.
By design, we've chosen $Z_1 \equiv Z_{\text{mod}}$ such that the signal gain from the node $V_{\text{mod}}$ is unity.
This reduces Eq.~(\ref{Eq:NG}) to
\begin{align}
\label{Eq:RedNG}
NG(s) &= 2 + \frac{Z_1}{R_2}
\end{align}

The op-amp noise is parametrized by two noise contributions -- $e_n$, the input voltage noise power spectral density (PSD), and $i_n$, the input current noise PSD. 
For the LM7171, $e_n = \SI[per-mode=symbol]{14}{\nano\volt\per\sqrthz}$ and $i_n = \SI[per-mode=symbol]{1.5}{\pico\ampere\per\sqrthz}$ at $\SI{10}{\kilo\hertz}$.
The voltage noise is summed in at the non-inverting input, while the current noise is present at both inputs.
To convert $i_n$ to an equivalent voltage noise $e_n$, we multiply by the impedances $Z_n$, $Z_p$ seen by the inverting and non-inverting nodes, respectively.
These are calculated as
\begin{align}
\begin{split}
\label{Eq:ZnZp}
Z_n &= Z_1 \epar Z_{\text{mod}} \epar  R_2   = \frac{Z_1}{2} \epar R_2 \\
Z_p &= R_{\text{LP}}  \big|\big|\frac{1}{s~C_{\text{LP}}}
\end{split}
\end{align}
The total noise contribution of the op-amp (referenced to the output) is
\begin{align}
\label{Eq:OpAmpNoise}
e_{n,\text{op-amp}} &= NG(s)\sqrt{e_n^2 + (Z_n i_n)^2 + (Z_p i_n)^2}
\end{align}

>>>>

The low-noise stabilization circuit is crucial to the performance of the design, as it is responsible for removing noise at the output of the flyback converter.
To accomplish this task, a high slew-rate op-amp (Texas Instruments LM7171, \SI[per-mode=symbol]{4100}{\volt\per\micro\second}) drives the galvanically isolated ground node of the flyback converter (see U2 in Fig.~\ref{Fig:PiezoCircuit}).
This op-amp enforces the HV output voltage
\begin{align}
\text{V}_\text{HV} &= \left(1 + \frac{R_1}{R_2~||~R_\text{mod}}\right) \text{V}_\text{DC} -
\left(\frac{R_\text{mod}}{R_1}\right) \text{V}_\text{mod}
\end{align}
We choose $R_1, R_\text{mod} = \SI{1}{\mega\ohm}$, $R_2 = \SI{20.5}{\kilo\ohm}$ such that the DC gain is $\approx 50$ and the modulation gain is unity.
Depending on the application, however, other gain configurations would work equally well provided the non-inverting gain of U2 closely matches the gain of the flyback regulator since they derive from the same control voltage.
Ultimately, the op-amp U2 sets the operating voltage of the output referenced to true circuit ground, while the flyback converter regulates the high voltage relative to the pseudoground node $\text{GND}_\text{HV}$.
Because the output of the flyback regulator is galvanically isolated, U2 is free to control the $\text{GND}_\text{HV}$ node at ``low'' voltages, which are transferred directly to the high voltage output.

@@

\begin{figure}[t]
\includegraphics[width=\columnwidth]{fig/NoiseModel.ai}
\caption{Noise model. \label{Fig:NoiseModel}}
\end{figure}
\begin{figure}[t]
\includegraphics[width=\columnwidth]{calc/NoiseContrib.pdf}
\caption{Noise Contributions (color online).  Plotted are the noise contributions from each source in our model -- op-amp current noise (dashed orange) and voltage noise (dotted blue); Johnson noise (dash-dotted green), DAC noise (long dashed red), and total noise (solid purple). Power spectral density is referred to the high voltage output.\label{Fig:NoisePlot}}
\end{figure}

We analyze the noise performance of the circuit according to the model shown in Fig.~\ref{Fig:NoiseModel}, where noise spectral densities are calculated at the node HV.
A summary of each noise contribution (op-amp, DAC, Johnson-Nyquist, external modulation input) is shown in Table~\ref{Tab:noise}, along with the cumulative root-mean-square (RMS) nose estimates in different frequency bands.
% We also discuss, given our choice of op-amp, the noise rejection ratio from the DRV2700 flyback regulator.
% -- not sure about how to do this... could just report the measured value:

To treat the intrinsic op-amp noise contributions, we first compute the noise gain ($NG$) for this amplifier configuration according to
\begin{align}
\label{Eq:NG}
NG(s) &= 1 + \frac{Z_1}{R_2 \epar Z_{\text{mod}}}\,,
\end{align}
where we've defined the equivalent impedances $Z_1 = R_1/(1+R_1 C_1 s)$ and $Z_{\text{mod}} = R_{\text{mod}}/(1+R_{\text{mod}} C_{\text{mod}} s)$, and $s = i\omega$ is the frequency in the Laplace domain.
By design, we've chosen $Z_1 \equiv Z_{\text{mod}}$ such that the signal gain from the node $V_{\text{mod}}$ is unity.
This reduces Eq.~(\ref{Eq:NG}) to
\begin{align}
\label{Eq:RedNG}
NG(s) &= 2 + \frac{Z_1}{R_2}\,.
\end{align}

The op-amp noise is parametrized by two noise contributions -- $e_n$, the input voltage noise power spectral density (PSD), and $i_n$, the input current noise PSD.
For the LM7171, $e_n = \SI[per-mode=symbol]{14}{\nano\volt\per\sqrthz}$ and $i_n = \SI[per-mode=symbol]{1.5}{\pico\ampere\per\sqrthz}$ at $\SI{10}{\kilo\hertz}$, with a $1/f$ noise character below this frequency~\cite{LM7171Datasheet}.
The voltage noise is summed in at the non-inverting input, while the current noise is present at both inputs.
To convert $i_n$ to an equivalent voltage noise $e_n$, we multiply by the impedances $Z_n$, $Z_p$ seen by the inverting and non-inverting nodes, respectively.
These are calculated as
\begin{align}
\begin{split}
\label{Eq:ZnZp}
Z_n &= Z_1 \epar Z_{\text{mod}} \epar  R_2   = \frac{Z_1}{2} \epar R_2 \\
Z_p &= R_{\text{LP}}  \big|\big|\frac{1}{s~C_{\text{LP}}}
\end{split}
\end{align}
The total noise contribution of the op-amp (referenced to the output) is
\begin{align}
\label{Eq:OpAmpNoise}
e_{n,\text{op-amp}} &= NG(s)\sqrt{e_n^2 + (Z_n i_n)^2 + (Z_p i_n)^2}
\end{align}
